\vspace{\baselineskip} The population of long-period transiting exoplanets \vspace{-2.5\baselineskip}

### 2016-07-27 document/ms.tex
adding window function figure

% \acknowledgments
\vspace{1.5em}
It is a pleasure to thank
Jeff Coughlin,
So Hattori,
Heather Knutson,
Hans-Walter Rix,
Dun Wang,
and
Angie Wolfgang
for helpful contributions to the ideas and code presented here.

>>>>

% \acknowledgments
\vspace{1.5em}
It is a pleasure to thank
Jeff Coughlin,
So Hattori,
Heather Knutson,
Hans-Walter Rix,
Dun Wang,
and
Angie Wolfgang
for helpful discussions and contributions.
